Viscous Transport in Eroding Porous Media

### 2019-08-07 docs/transport/erosion_transport.tex
add new figs in transport paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 nearly touching bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider 20 eroding bodies that are discretized with $N_\iin=256$
points and are initially placed in $[-1,1] \times [-1,1]$.  The
background flow is the Hagen-Poiseuille flow
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right],
\end{align}
where the flow rate $U$ is chosen so that the pressure drop from $x=-2$
to $x=2$ is held fixed at 2.  We start by analyzing the effect of
erosion on the area fraction and the flow rate.  In
Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
function of normalized time.  Initially, 62\% of the geometry is eroded
bodies corresponding to a porosity of $0.38$, and the area fraction
decreases to 0 as the bodies erode.  The trend of the area fraction
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(a)),
but with a larger initial area fraction.  We also compute the flow rate
$U$ required to maintain a constant pressure drop across the channel in
Figure~\ref{fig:Eroding20flowrate}(b).  Again, the trend of $U$
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(b)),
except that the initial flow rate is an order of magnitude smaller
because of the larger initial area fraction.  Starting around normalized
time $0.2$, Figure~\ref{fig:Eroding20flowrate}(b) is roughly linear
which indicates that the flow rate can be written as a power law.  Using
a line of best fit, the flow rate is approximately 
\begin{align} 
  U \approx \left(\frac{t}{t_f}\right)^{3.43},
\end{align}
which is the dashed line in Figure~\ref{fig:Eroding20flowrate}(b).

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 Bodies at a Medium Porosity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider 20 eroding bodies that are discretized with $N_\iin=256$
points and are initially placed in $[-1,1] \times [-1,1]$.  The
background flow is the Hagen-Poiseuille flow
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right],
\end{align}
where the flow rate $U$ is chosen so that the pressure drop from $x=-2$
to $x=2$ is held fixed at 2.  We start by analyzing the effect of
erosion on the area fraction and the flow rate.  In
Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
function of normalized time.  Initially, 62\% of the geometry is eroded
bodies corresponding to a porosity of $0.38$, and the area fraction
decreases to 0 as the bodies erode.  The trend of the area fraction
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(a)),
but with a larger initial area fraction.  We also compute the flow rate
$U$ required to maintain a constant pressure drop across the channel in
Figure~\ref{fig:Eroding20flowrate}(b).  Again, the trend of $U$
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(b)),
except that the initial flow rate is an order of magnitude smaller
because of the larger initial area fraction.  Starting around normalized
time $0.2$, Figure~\ref{fig:Eroding20flowrate}(b) is roughly linear
which indicates that the flow rate can be written as a power law.  Using
a line of best fit, the flow rate is approximately 
\begin{align} 
  U \approx \left(\frac{t}{t_f}\right)^{3.43},
\end{align}
which is the dashed line in Figure~\ref{fig:Eroding20flowrate}(b).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 Bodies at a Low Porosity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\begin{center}
  \includegraphics[height=0.225\textwidth]{./figs/20b2_vort1}
  \includegraphics[height=0.225\textwidth]{./figs/20b2_vort150}
  \includegraphics[height=0.225\textwidth]{./figs/20b2_vort300}
  \includegraphics[height=0.225\textwidth]{./figs/20b2_vort450}
\caption{\label{fig:ErodingLow20vort} Erosion of 20 nearly touching bodies
with the fixed pressure drop condition. The color is the vorticity of
the fluid. The 4 snapshots are evenly spaced in time. We use $N_\iin =
256$ discretization points on the body, a time-step of $\Dt=10^{-4}$,
and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $. }
\end{center}
\end{figure}

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian20b}
\caption{\label{fig:ErodingLow20tort} The tortuosity inside of an
eroding geometry initialized with 20 bodies.  The tortuosity is
calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue dots).
The dash line is the fitting line $\hat{T}(\phi)=\phi^p$ as $p=-0.1669$ and 
the root mean square deviation is $1.13 \times 10^{-2}$.}
\end{figure}
